%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Aditya Mane} \\[7.5pt]
\href{https://github.com/Aditya-Mane0411}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{https://www.linkedin.com/in/aditya-mane-36831826b/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{https://aditya-portfolio-orcin-iota.vercel.app/}{\raisebox{-0.05\height}\faGlobe \ Portfolio} \ $|$ \ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
Enthusiastic Computer Science undergraduate specializing in Cybersecurity, aspiring to enhance technical and analytical skills through practical software development experience. Looking to contribute to real-world projects, learn from industry professionals, and build a strong foundation for a successful technology career.

%Experience
\section{Internship Experience}

\begin{joblong}{Developer Intern (Erfinden Technologies)}{June 2025 - July 2025}
\item Developed and deployed a full-stack B2B Agribusiness marketplace with multilingual support and data-driven insights.
\item Designed a responsive front-end using ReactJS (TypeScript, Tailwind, Vite) for a seamless user experience.
\item Integrated Supabase for backend services including authentication, real-time database operations, and PostgreSQL management.
\item Conducted Python-based web scraping and data analysis to gather competitor insights and inform product improvements.

\end{joblong}



\begin{joblong}{Full Stack Web Development Intern (Placify Technologies)}{June 2024 - July 2024}
\item Designed and deployed a personal portfolio website highlighting technical projects, achievements, and certifications.
\item Built and maintained responsive user interfaces using HTML, CSS, JavaScript, and Bootstrap to enhance usability and performance.
\item Ensured cross-browser compatibility and seamless rendering across varied screen sizes and devices.

\end{joblong}

\begin{joblong}{Cybersecurity Intern (Cyber Vidyapeeth)}{June 2023 - July 2023}
\item Implemented cybersecurity basics in actual live projects using Kali Linux.
\item Explored tools and techniques used in ethical hacking, OSINT (Open Source Intelligence), and vulnerability assessment.
\item Developed a reverse-IP lookup tool using python frameworks.

\end{joblong}
  
%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Portfolio Website} & \hfill \href{https://aditya-portfolio-orcin-iota.vercel.app/}{Portfolio Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{ personal portfolio website, designed and developed to showcase your skills, projects, experience, and achievements in a modern, interactive format. Built with a responsive design to ensure seamless access across devices, the site features sections. The website serves as a professional digital presence — enabling visitors to quickly understand my profile, review my work, and get in touch}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{OWASP Risk Calculator} & \hfill \href{https://some-link.com}{GitHub Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{A Python- and Flask-based web application designed to assess and manage web security risks. It enables users to input vulnerability details, automatically calculate risk levels based on likelihood and impact, and generate tailored mitigation suggestions.}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Insta Miner} & \hfill \href{https://some-link.com}{GitHub Link} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{An Instagram Profile Scraper built using Streamlit and Instaloader that enables users to fetch and view public Instagram profile details by simply entering a username. It displays key information such as the user’s ID, bio, follower and following counts, post count, and external links. Developed in Python, it leverages Streamlit for the interactive interface, Instaloader for data extraction, and the OS module for file handling}  \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	

    % 2030 - present & PhD (Subject) at \textbf{University} \hfill \normalsize (GPA: 4.0/4.0) \\
    % 2023 - 2027 & Bachelor's Degree at \textbf{College} \hfill (GPA: 4.0/4.0) \\ 
    % 2022 & Class 12th Some Board \hfill  (Grades) \\
    % 2021 & Class 10th Some Board \hfill  (Grades) \\

    \textbf{Symbiosis Skills and Professional University} & \hfill July 2026 - Aug 2022 \\ \vspace*{2mm}
    B.Tech CSIT - 8.5 CGPA \\ 
    
  \textbf{H.B. Girme Junior College} & \hfill Aug 2020 - June 2022 \\ \vspace*{2mm}
    Higher Education in IT - 83\% \\ 
    
    \textbf{Sri Sri Ravishankar Vidya Mandir} & \hfill May 2020 \\ \vspace*{2mm}
    CBSE - 78\% \\

\end{tabularx}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
%\section{Publications}
%\begin{refsection}[citations.bib]
%\nocite{*}
%\printbibliography[heading=none]
%\end{refsection} 

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming Languages} & \normalsize{Python, HTML, CSS, Java, JavaScript (ReactJS, Angular, Node.js)} \\

\textbf{Frameworks \& Tools} & \normalsize{Flask, Django, Bootstrap, Tkinter, Scikit-learn, Pandas, NumPy, Matplotlib} \\  

\textbf{Software Development} & \normalsize{OOP, Git/GitHub, Streamlit, Jira Software} \\

\textbf{Other Tools} & \normalsize{Google Workspace, Cloud Computing, Generative AI, AWS} \\
\end{tabularx}


\vfill
\center{\footnotesize Last updated: \today}

\end{document}
